### 2017-03-11 thesis/misc/appendix.tex
Really finished the draft for appendix A - tmp commit

>>>>

	\section{Remainder of the results of the other CR obesity metagenes in CR data set}
	\label{sec:rest_of_the_cr_ob_meta_heatmap_results}

	As already mentioned in \cref{sub:_novel_obesity_associated_signatures_and_sample_bmi}, all of the obesity associated geneti signatures derived from the CR data captured the overall gene expressions in the CR data, and significantly correlated with the sample \gls{bmi}/\gls{bmi} status (\cref{fig:appendix/cr_ob_meta_heatmap,fig:appendix/cr_ob_meta_box_scatter}).

	\begin{figure}[htp!]
		\centering
		\includegraphics[width=0.45\linewidth,page=8]{appendix/cr_deg_meta_vs_clin}\\
		\vspace{1em}
		\includegraphics[width=0.45\linewidth,page=13]{appendix/cr_deg_meta_vs_clin}
		\hfill
		\includegraphics[width=0.45\linewidth,page=18]{appendix/cr_deg_meta_vs_clin}\\
		\vspace{1em}
		\includegraphics[width=0.45\linewidth,page=23]{appendix/cr_deg_meta_vs_clin}
		\hfill
		\includegraphics[width=0.45\linewidth,page=28]{appendix/cr_deg_meta_vs_clin}\\
		\caption{Heatmaps showing the association of the other CR obesity metagenes with the sample gene expression from the CR data set.
	Scales are as described in previous figures.}
		\label{fig:appendix/cr_ob_meta_heatmap}
	\end{figure}

	\begin{figure}[htpb]
		\ContinuedFloat
		\captionsetup{list=off,format=cont}
		\centering
		\includegraphics[width=0.45\linewidth,page=33]{appendix/cr_deg_meta_vs_clin}
		\hfill
		\includegraphics[width=0.45\linewidth,page=38]{appendix/cr_deg_meta_vs_clin}\\
		\vspace{1em}
		\caption{figure}
	\end{figure}

	\begin{figure}[htpb]
		\centering
		\includegraphics[page=9,width=0.45\linewidth]{appendix/cr_deg_meta_vs_clin}
		\hfill
		\includegraphics[page=10,width=0.45\linewidth]{appendix/cr_deg_meta_vs_clin}\\
		\caption{Box plots and scatter plots showing the association of the other CR obesity metagenes with the sample \gls{bmi} status  and \gls{bmi} from the CR data set, respectively.
	P-values and $R^2$-value are as described in previous figures.}
		\label{fig:appendix/cr_ob_meta_box_scatter}
	\end{figure}

	\begin{figure}[htpb]
		\ContinuedFloat
		\captionsetup{list=off,format=cont}
		\centering
		\includegraphics[page=14,width=0.45\linewidth]{appendix/cr_deg_meta_vs_clin}
		\hfill
		\includegraphics[page=15,width=0.45\linewidth]{appendix/cr_deg_meta_vs_clin}\\
		\includegraphics[page=19,width=0.45\linewidth]{appendix/cr_deg_meta_vs_clin}
		\hfill
		\includegraphics[page=20,width=0.45\linewidth]{appendix/cr_deg_meta_vs_clin}\\
		\includegraphics[page=24,width=0.45\linewidth]{appendix/cr_deg_meta_vs_clin}
		\hfill
		\includegraphics[page=25,width=0.45\linewidth]{appendix/cr_deg_meta_vs_clin}\\
		\caption{Name}
	\end{figure}

	\begin{figure}[htpb]
		\ContinuedFloat
		\captionsetup{list=off,format=cont}
		\centering
		\includegraphics[page=29,width=0.45\linewidth]{appendix/cr_deg_meta_vs_clin}
		\hfill
		\includegraphics[page=30,width=0.45\linewidth]{appendix/cr_deg_meta_vs_clin}\\
		\includegraphics[page=34,width=0.45\linewidth]{appendix/cr_deg_meta_vs_clin}
		\hfill
		\includegraphics[page=35,width=0.45\linewidth]{appendix/cr_deg_meta_vs_clin}\\
		\includegraphics[page=39,width=0.45\linewidth]{appendix/cr_deg_meta_vs_clin}
		\hfill
		\includegraphics[page=40,width=0.45\linewidth]{appendix/cr_deg_meta_vs_clin}\\
		\caption{Name}
	\end{figure}

	\section{Remainder of the results of the other CR obesity metagenes in \gls{icgc} data sets}
	\label{sec:rest_of_the_cr_ob_meta_heatmap_results_icgc}

	In the \gls{icgc} data sets, \gls{blca} data set was the only \gls{icgc} data set to show any significant association with the sample \gls{bmi} status.
	All of the other \gls{icgc} cancer data sets showed no significant association with the sample \gls{bmi}/\gls{bmi} status, but the metagenes were reflective of the sample gene expressions in all of the cancer types.
	For clarity and convenience, results will be split based on the \gls{icgc} cancer type.

	\subsubsection{\gls{blca}}
	\label{ssub:blca}

	\begin{figure}[htp!]
		\centering
		\includegraphics[page=3,width=0.45\linewidth]{appendix/crolgene_ICGC}\\
		\vspace{1em}
		\includegraphics[page=3,width=0.45\linewidth]{appendix/resobsgene_ICGC}
		\hfill
		\includegraphics[page=3,width=0.45\linewidth]{appendix/rescrolgene_ICGC}\\
		\caption{Heatmaps showing the association of the other CR obesity metagenes with the sample gene expression from the \gls{icgc} \gls{blca} data set.
		Scales, p-values and $R^2$-value are as described in previous figures.}
		\label{fig:degmetaicgc_blca}
	\end{figure}

	\begin{figure}[htpb]
		\ContinuedFloat
		\captionsetup{list=off,format=cont}
		\centering
		\includegraphics[page=3,height=0.43\linewidth,width=0.45\linewidth]{appendix/caobsgene_ICGC}
		\hfill
		\includegraphics[page=3,height=0.43\linewidth,width=0.45\linewidth]{appendix/cacrolgene_ICGC}\\
		\includegraphics[page=3,height=0.43\linewidth,width=0.45\linewidth]{appendix/caresobsgene_ICGC}
		\hfill
		\includegraphics[page=3,height=0.43\linewidth,width=0.45\linewidth]{appendix/carescrolgene_ICGC}\\
		\caption{Name}
	\end{figure}

	\begin{figure}[htpb]
		\centering
		\includegraphics[page=4,width=0.45\linewidth]{appendix/crolgene_ICGC}
		\hfill
		\includegraphics[page=5,width=0.45\linewidth]{appendix/crolgene_ICGC}\\
		\caption{Box plots and scatter plots showing the association of the other CR obesity metagenes with the sample \gls{bmi} status  and \gls{bmi} from the \gls{icgc} \gls{blca} data set, respectively.
	P-values and $R^2$-value are as described in previous figures.}
		\label{fig:appendix/cr_ob_meta_box_scatter_blca}
	\end{figure}

	\begin{figure}[htpb]
		\ContinuedFloat
		\captionsetup{list=off,format=cont}
		\centering
		\includegraphics[page=4,width=0.45\linewidth]{appendix/resobsgene_ICGC}
		\hfill
		\includegraphics[page=5,width=0.45\linewidth]{appendix/resobsgene_ICGC}\\
		\includegraphics[page=4,width=0.45\linewidth]{appendix/rescrolgene_ICGC}
		\hfill
		\includegraphics[page=5,width=0.45\linewidth]{appendix/rescrolgene_ICGC}\\
		\includegraphics[page=4,width=0.45\linewidth]{appendix/caobsgene_ICGC}
		\hfill
		\includegraphics[page=5,width=0.45\linewidth]{appendix/caobsgene_ICGC}\\
		\caption{Name}
	\end{figure}

	\begin{figure}[htpb]
		\ContinuedFloat
		\captionsetup{list=off,format=cont}
		\centering
		\includegraphics[page=4,width=0.45\linewidth]{appendix/cacrolgene_ICGC}
		\hfill
		\includegraphics[page=5,width=0.45\linewidth]{appendix/cacrolgene_ICGC}\\
		\includegraphics[page=4,width=0.45\linewidth]{appendix/caresobsgene_ICGC}
		\hfill
		\includegraphics[page=5,width=0.45\linewidth]{appendix/caresobsgene_ICGC}\\
		\includegraphics[page=4,width=0.45\linewidth]{appendix/carescrolgene_ICGC}
		\hfill
		\includegraphics[page=5,width=0.45\linewidth]{appendix/carescrolgene_ICGC}\\
		\caption{Name}
	\end{figure}

	\newpage

	\subsubsection{\gls{cesc}}
	\label{ssub:cesc}

	\begin{figure}[htp!]
		\centering
		\includegraphics[page=8,height=0.43\linewidth,width=0.45\linewidth]{appendix/rawobsgene_ICGC}
		\hfill
		\includegraphics[page=8,height=0.43\linewidth,width=0.45\linewidth]{appendix/crolgene_ICGC}\\
		\includegraphics[page=8,height=0.43\linewidth,width=0.45\linewidth]{appendix/resobsgene_ICGC}
		\hfill
		\includegraphics[page=8,height=0.43\linewidth,width=0.45\linewidth]{appendix/rescrolgene_ICGC}\\
		\includegraphics[page=8,height=0.43\linewidth,width=0.45\linewidth]{appendix/caobsgene_ICGC}
		\hfill
		\includegraphics[page=8,height=0.43\linewidth,width=0.45\linewidth]{appendix/cacrolgene_ICGC}\\
		\caption{Heatmaps showing the association of the other CR obesity metagenes with the sample gene expression from the \gls{icgc} \gls{cesc} data set.
		Scales, p-values and $R^2$-value are as described in previous figures.}
		\label{fig:degmetaicgc_cesc}
	\end{figure}

	\begin{figure}[htpb]
		\ContinuedFloat
		\captionsetup{list=off,format=cont}
		\centering
		\includegraphics[page=8,height=0.42\linewidth,width=0.45\linewidth]{appendix/caresobsgene_ICGC}
		\hfill
		\includegraphics[page=8,height=0.42\linewidth,width=0.45\linewidth]{appendix/carescrolgene_ICGC}\\
		\caption{Name}
	\end{figure}

	\begin{figure}[!htpb]
		\centering
		\includegraphics[page=9,width=0.40\linewidth]{appendix/rawobsgene_ICGC}
		\hfill
		\includegraphics[page=10,width=0.40\linewidth]{appendix/rawobsgene_ICGC}\\
		\includegraphics[page=9,width=0.40\linewidth]{appendix/crolgene_ICGC}
		\hfill
		\includegraphics[page=10,width=0.40\linewidth]{appendix/crolgene_ICGC}\\
		\caption{Box plots and scatter plots showing the association of the other CR obesity metagenes with the sample \gls{bmi} status  and \gls{bmi} from the \gls{icgc} \gls{cesc} data set, respectively.
	P-values and $R^2$-value are as described in previous figures.}
		\label{fig:appendix/cr_ob_meta_box_scatter_cesc}
	\end{figure}

	\begin{figure}[htpb]
		\ContinuedFloat
		\captionsetup{list=off,format=cont}
		\centering
		\includegraphics[page=9,width=0.45\linewidth]{appendix/resobsgene_ICGC}
		\hfill
		\includegraphics[page=10,width=0.45\linewidth]{appendix/resobsgene_ICGC}\\
		\includegraphics[page=9,width=0.45\linewidth]{appendix/rescrolgene_ICGC}
		\hfill
		\includegraphics[page=10,width=0.45\linewidth]{appendix/rescrolgene_ICGC}\\
		\includegraphics[page=9,width=0.45\linewidth]{appendix/caobsgene_ICGC}
		\hfill
		\includegraphics[page=10,width=0.45\linewidth]{appendix/caobsgene_ICGC}\\
		\caption{Name}
	\end{figure}

	\begin{figure}[htpb]
		\ContinuedFloat
		\captionsetup{list=off,format=cont}
		\centering
		\includegraphics[page=9,width=0.45\linewidth]{appendix/cacrolgene_ICGC}
		\hfill
		\includegraphics[page=10,width=0.45\linewidth]{appendix/cacrolgene_ICGC}\\
		\includegraphics[page=9,width=0.45\linewidth]{appendix/caresobsgene_ICGC}
		\hfill
		\includegraphics[page=10,width=0.45\linewidth]{appendix/caresobsgene_ICGC}\\
		\includegraphics[page=9,width=0.45\linewidth]{appendix/carescrolgene_ICGC}
		\hfill
		\includegraphics[page=10,width=0.45\linewidth]{appendix/carescrolgene_ICGC}\\
		\caption{Name}
	\end{figure}

	\newpage

	\subsubsection{\gls{coad}}
	\label{ssub:coad}

	\begin{figure}[htp!]
		\centering
		\includegraphics[page=13,height=0.43\linewidth,width=0.45\linewidth]{appendix/rawobsgene_ICGC}
		\hfill
		\includegraphics[page=13,height=0.43\linewidth,width=0.45\linewidth]{appendix/crolgene_ICGC}\\
		\includegraphics[page=13,height=0.43\linewidth,width=0.45\linewidth]{appendix/resobsgene_ICGC}
		\hfill
		\includegraphics[page=13,height=0.43\linewidth,width=0.45\linewidth]{appendix/rescrolgene_ICGC}\\
		\includegraphics[page=13,height=0.43\linewidth,width=0.45\linewidth]{appendix/caobsgene_ICGC}
		\hfill
		\includegraphics[page=13,height=0.43\linewidth,width=0.45\linewidth]{appendix/cacrolgene_ICGC}\\
		\caption{Heatmaps showing the association of the other CR obesity metagenes with the sample gene expression from the \gls{icgc} \gls{coad} data set.
		Scales, p-values and $R^2$-value are as described in previous figures.}
		\label{fig:degmetaicgc_coad}
	\end{figure}

	\begin{figure}[htpb]
		\ContinuedFloat
		\captionsetup{list=off,format=cont}
		\centering
		\includegraphics[page=13,height=0.42\linewidth,width=0.45\linewidth]{appendix/caresobsgene_ICGC}
		\hfill
		\includegraphics[page=13,height=0.42\linewidth,width=0.45\linewidth]{appendix/carescrolgene_ICGC}\\
		\caption{Name}
	\end{figure}

	\begin{figure}[!htpb]
		\centering
		\includegraphics[page=14,width=0.40\linewidth]{appendix/rawobsgene_ICGC}
		\hfill
		\includegraphics[page=15,width=0.40\linewidth]{appendix/rawobsgene_ICGC}\\
		\includegraphics[page=14,width=0.40\linewidth]{appendix/crolgene_ICGC}
		\hfill
		\includegraphics[page=15,width=0.40\linewidth]{appendix/crolgene_ICGC}\\
		\caption{Box plots and scatter plots showing the association of the other CR obesity metagenes with the sample \gls{bmi} status  and \gls{bmi} from the \gls{icgc} \gls{coad} data set, respectively.
	P-values and $R^2$-value are as described in previous figures.}
		\label{fig:appendix/cr_ob_meta_box_scatter_coad}
	\end{figure}

	\begin{figure}[htpb]
		\ContinuedFloat
		\captionsetup{list=off,format=cont}
		\centering
		\includegraphics[page=14,width=0.45\linewidth]{appendix/resobsgene_ICGC}
		\hfill
		\includegraphics[page=15,width=0.45\linewidth]{appendix/resobsgene_ICGC}\\
		\includegraphics[page=14,width=0.45\linewidth]{appendix/rescrolgene_ICGC}
		\hfill
		\includegraphics[page=15,width=0.45\linewidth]{appendix/rescrolgene_ICGC}\\
		\includegraphics[page=14,width=0.45\linewidth]{appendix/caobsgene_ICGC}
		\hfill
		\includegraphics[page=15,width=0.45\linewidth]{appendix/caobsgene_ICGC}\\
		\caption{Name}
	\end{figure}

	\begin{figure}[htpb]
		\ContinuedFloat
		\captionsetup{list=off,format=cont}
		\centering
		\includegraphics[page=14,width=0.45\linewidth]{appendix/cacrolgene_ICGC}
		\hfill
		\includegraphics[page=15,width=0.45\linewidth]{appendix/cacrolgene_ICGC}\\
		\includegraphics[page=14,width=0.45\linewidth]{appendix/caresobsgene_ICGC}
		\hfill
		\includegraphics[page=15,width=0.45\linewidth]{appendix/caresobsgene_ICGC}\\
		\includegraphics[page=14,width=0.45\linewidth]{appendix/carescrolgene_ICGC}
		\hfill
		\includegraphics[page=15,width=0.45\linewidth]{appendix/carescrolgene_ICGC}\\
		\caption{Name}
	\end{figure}

	\newpage

	\subsubsection{\gls{kirp}}
	\label{ssub:kirp}

	\begin{figure}[htp!]
		\centering
		\includegraphics[page=18,height=0.43\linewidth,width=0.45\linewidth]{appendix/rawobsgene_ICGC}
		\hfill
		\includegraphics[page=18,height=0.43\linewidth,width=0.45\linewidth]{appendix/crolgene_ICGC}\\
		\includegraphics[page=18,height=0.43\linewidth,width=0.45\linewidth]{appendix/resobsgene_ICGC}
		\hfill
		\includegraphics[page=18,height=0.43\linewidth,width=0.45\linewidth]{appendix/rescrolgene_ICGC}\\
		\includegraphics[page=18,height=0.43\linewidth,width=0.45\linewidth]{appendix/caobsgene_ICGC}
		\hfill
		\includegraphics[page=18,height=0.43\linewidth,width=0.45\linewidth]{appendix/cacrolgene_ICGC}\\
		\caption{Heatmaps showing the association of the other CR obesity metagenes with the sample gene expression from the \gls{icgc} \gls{kirp} data set.
		Scales, p-values and $R^2$-value are as described in previous figures.}
		\label{fig:degmetaicgc_kirp}
	\end{figure}

	\begin{figure}[htpb]
		\ContinuedFloat
		\captionsetup{list=off,format=cont}
		\centering
		\includegraphics[page=18,height=0.42\linewidth,width=0.45\linewidth]{appendix/caresobsgene_ICGC}
		\hfill
		\includegraphics[page=18,height=0.42\linewidth,width=0.45\linewidth]{appendix/carescrolgene_ICGC}\\
		\caption{Name}
	\end{figure}

	\begin{figure}[!htpb]
		\centering
		\includegraphics[page=19,width=0.40\linewidth]{appendix/rawobsgene_ICGC}
		\hfill
		\includegraphics[page=20,width=0.40\linewidth]{appendix/rawobsgene_ICGC}\\
		\includegraphics[page=19,width=0.40\linewidth]{appendix/crolgene_ICGC}
		\hfill
		\includegraphics[page=20,width=0.40\linewidth]{appendix/crolgene_ICGC}\\
		\caption{Box plots and scatter plots showing the association of the other CR obesity metagenes with the sample \gls{bmi} status  and \gls{bmi} from the \gls{icgc} \gls{kirp} data set, respectively.
	P-values and $R^2$-value are as described in previous figures.}
		\label{fig:appendix/cr_ob_meta_box_scatter_kirp}
	\end{figure}

	\begin{figure}[htpb]
		\ContinuedFloat
		\captionsetup{list=off,format=cont}
		\centering
		\includegraphics[page=19,width=0.45\linewidth]{appendix/resobsgene_ICGC}
		\hfill
		\includegraphics[page=20,width=0.45\linewidth]{appendix/resobsgene_ICGC}\\
		\includegraphics[page=19,width=0.45\linewidth]{appendix/rescrolgene_ICGC}
		\hfill
		\includegraphics[page=20,width=0.45\linewidth]{appendix/rescrolgene_ICGC}\\
		\includegraphics[page=19,width=0.45\linewidth]{appendix/caobsgene_ICGC}
		\hfill
		\includegraphics[page=20,width=0.45\linewidth]{appendix/caobsgene_ICGC}\\
		\caption{Name}
	\end{figure}

	\begin{figure}[htpb]
		\ContinuedFloat
		\captionsetup{list=off,format=cont}
		\centering
		\includegraphics[page=19,width=0.45\linewidth]{appendix/cacrolgene_ICGC}
		\hfill
		\includegraphics[page=20,width=0.45\linewidth]{appendix/cacrolgene_ICGC}\\
		\includegraphics[page=19,width=0.45\linewidth]{appendix/caresobsgene_ICGC}
		\hfill
		\includegraphics[page=20,width=0.45\linewidth]{appendix/caresobsgene_ICGC}\\
		\includegraphics[page=19,width=0.45\linewidth]{appendix/carescrolgene_ICGC}
		\hfill
		\includegraphics[page=20,width=0.45\linewidth]{appendix/carescrolgene_ICGC}\\
		\caption{Name}
	\end{figure}

	\newpage

	\subsubsection{\gls{lihc}}
	\label{ssub:lihc}

	\begin{figure}[htp!]
		\centering
		\includegraphics[page=23,height=0.43\linewidth,width=0.45\linewidth]{appendix/rawobsgene_ICGC}
		\hfill
		\includegraphics[page=23,height=0.43\linewidth,width=0.45\linewidth]{appendix/crolgene_ICGC}\\
		\includegraphics[page=23,height=0.43\linewidth,width=0.45\linewidth]{appendix/resobsgene_ICGC}
		\hfill
		\includegraphics[page=23,height=0.43\linewidth,width=0.45\linewidth]{appendix/rescrolgene_ICGC}\\
		\includegraphics[page=23,height=0.43\linewidth,width=0.45\linewidth]{appendix/caobsgene_ICGC}
		\hfill
		\includegraphics[page=23,height=0.43\linewidth,width=0.45\linewidth]{appendix/cacrolgene_ICGC}\\
		\caption{Heatmaps showing the association of the other CR obesity metagenes with the sample gene expression from the \gls{icgc} \gls{lihc} data set.
		Scales, p-values and $R^2$-value are as described in previous figures.}
		\label{fig:degmetaicgc_lihc}
	\end{figure}

	\begin{figure}[htpb]
		\ContinuedFloat
		\captionsetup{list=off,format=cont}
		\centering
		\includegraphics[page=23,height=0.42\linewidth,width=0.45\linewidth]{appendix/caresobsgene_ICGC}
		\hfill
		\includegraphics[page=23,height=0.42\linewidth,width=0.45\linewidth]{appendix/carescrolgene_ICGC}\\
		\caption{Name}
	\end{figure}

	\begin{figure}[!htpb]
		\centering
		\includegraphics[page=24,width=0.40\linewidth]{appendix/rawobsgene_ICGC}
		\hfill
		\includegraphics[page=25,width=0.40\linewidth]{appendix/rawobsgene_ICGC}\\
		\includegraphics[page=24,width=0.40\linewidth]{appendix/crolgene_ICGC}
		\hfill
		\includegraphics[page=25,width=0.40\linewidth]{appendix/crolgene_ICGC}\\
		\caption{Box plots and scatter plots showing the association of the other CR obesity metagenes with the sample \gls{bmi} status  and \gls{bmi} from the \gls{icgc} \gls{lihc} data set, respectively.
	P-values and $R^2$-value are as described in previous figures.}
		\label{fig:appendix/cr_ob_meta_box_scatter_lihc}
	\end{figure}

	\begin{figure}[htpb]
		\ContinuedFloat
		\captionsetup{list=off,format=cont}
		\centering
		\includegraphics[page=24,width=0.45\linewidth]{appendix/resobsgene_ICGC}
		\hfill
		\includegraphics[page=25,width=0.45\linewidth]{appendix/resobsgene_ICGC}\\
		\includegraphics[page=24,width=0.45\linewidth]{appendix/rescrolgene_ICGC}
		\hfill
		\includegraphics[page=25,width=0.45\linewidth]{appendix/rescrolgene_ICGC}\\
		\includegraphics[page=24,width=0.45\linewidth]{appendix/caobsgene_ICGC}
		\hfill
		\includegraphics[page=25,width=0.45\linewidth]{appendix/caobsgene_ICGC}\\
		\caption{Name}
	\end{figure}

	\begin{figure}[htpb]
		\ContinuedFloat
		\captionsetup{list=off,format=cont}
		\centering
		\includegraphics[page=24,width=0.45\linewidth]{appendix/cacrolgene_ICGC}
		\hfill
		\includegraphics[page=25,width=0.45\linewidth]{appendix/cacrolgene_ICGC}\\
		\includegraphics[page=24,width=0.45\linewidth]{appendix/caresobsgene_ICGC}
		\hfill
		\includegraphics[page=25,width=0.45\linewidth]{appendix/caresobsgene_ICGC}\\
		\includegraphics[page=24,width=0.45\linewidth]{appendix/carescrolgene_ICGC}
		\hfill
		\includegraphics[page=25,width=0.45\linewidth]{appendix/carescrolgene_ICGC}\\
		\caption{Name}
	\end{figure}

	\newpage

	\subsubsection{\gls{read}}
	\label{ssub:read}

	\begin{figure}[htp!]
		\centering
		\includegraphics[page=28,height=0.43\linewidth,width=0.45\linewidth]{appendix/rawobsgene_ICGC}
		\hfill
		\includegraphics[page=28,height=0.43\linewidth,width=0.45\linewidth]{appendix/crolgene_ICGC}\\
		\includegraphics[page=28,height=0.43\linewidth,width=0.45\linewidth]{appendix/resobsgene_ICGC}
		\hfill
		\includegraphics[page=28,height=0.43\linewidth,width=0.45\linewidth]{appendix/rescrolgene_ICGC}\\
		\includegraphics[page=28,height=0.43\linewidth,width=0.45\linewidth]{appendix/caobsgene_ICGC}
		\hfill
		\includegraphics[page=28,height=0.43\linewidth,width=0.45\linewidth]{appendix/cacrolgene_ICGC}\\
		\caption{Heatmaps showing the association of the other CR obesity metagenes with the sample gene expression from the \gls{icgc} \gls{read} data set.
		Scales, p-values and $R^2$-value are as described in previous figures.}
		\label{fig:degmetaicgc_read}
	\end{figure}

	\begin{figure}[htpb]
		\ContinuedFloat
		\captionsetup{list=off,format=cont}
		\centering
		\includegraphics[page=28,height=0.42\linewidth,width=0.45\linewidth]{appendix/caresobsgene_ICGC}
		\hfill
		\includegraphics[page=28,height=0.42\linewidth,width=0.45\linewidth]{appendix/carescrolgene_ICGC}\\
		\caption{Name}
	\end{figure}

	\begin{figure}[!htpb]
		\centering
		\includegraphics[page=29,width=0.40\linewidth]{appendix/rawobsgene_ICGC}
		\hfill
		\includegraphics[page=30,width=0.40\linewidth]{appendix/rawobsgene_ICGC}\\
		\includegraphics[page=29,width=0.40\linewidth]{appendix/crolgene_ICGC}
		\hfill
		\includegraphics[page=30,width=0.40\linewidth]{appendix/crolgene_ICGC}\\
		\caption{Box plots and scatter plots showing the association of the other CR obesity metagenes with the sample \gls{bmi} status  and \gls{bmi} from the \gls{icgc} \gls{read} data set, respectively.
	P-values and $R^2$-value are as described in previous figures.}
		\label{fig:appendix/cr_ob_meta_box_scatter_read}
	\end{figure}

	\begin{figure}[htpb]
		\ContinuedFloat
		\captionsetup{list=off,format=cont}
		\centering
		\includegraphics[page=29,width=0.45\linewidth]{appendix/resobsgene_ICGC}
		\hfill
		\includegraphics[page=30,width=0.45\linewidth]{appendix/resobsgene_ICGC}\\
		\includegraphics[page=29,width=0.45\linewidth]{appendix/rescrolgene_ICGC}
		\hfill
		\includegraphics[page=30,width=0.45\linewidth]{appendix/rescrolgene_ICGC}\\
		\includegraphics[page=29,width=0.45\linewidth]{appendix/caobsgene_ICGC}
		\hfill
		\includegraphics[page=30,width=0.45\linewidth]{appendix/caobsgene_ICGC}\\
		\caption{Name}
	\end{figure}

	\begin{figure}[htpb]
		\ContinuedFloat
		\captionsetup{list=off,format=cont}
		\centering
		\includegraphics[page=29,width=0.45\linewidth]{appendix/cacrolgene_ICGC}
		\hfill
		\includegraphics[page=30,width=0.45\linewidth]{appendix/cacrolgene_ICGC}\\
		\includegraphics[page=29,width=0.45\linewidth]{appendix/caresobsgene_ICGC}
		\hfill
		\includegraphics[page=30,width=0.45\linewidth]{appendix/caresobsgene_ICGC}\\
		\includegraphics[page=29,width=0.45\linewidth]{appendix/carescrolgene_ICGC}
		\hfill
		\includegraphics[page=30,width=0.45\linewidth]{appendix/carescrolgene_ICGC}\\
		\caption{Name}
	\end{figure}

	\newpage

	\subsubsection{\gls{skcm}}
	\label{ssub:skcm}

	\begin{figure}[htp!]
		\centering
		\includegraphics[page=33,height=0.43\linewidth,width=0.45\linewidth]{appendix/rawobsgene_ICGC}
		\hfill
		\includegraphics[page=33,height=0.43\linewidth,width=0.45\linewidth]{appendix/crolgene_ICGC}\\
		\includegraphics[page=33,height=0.43\linewidth,width=0.45\linewidth]{appendix/resobsgene_ICGC}
		\hfill
		\includegraphics[page=33,height=0.43\linewidth,width=0.45\linewidth]{appendix/rescrolgene_ICGC}\\
		\includegraphics[page=33,height=0.43\linewidth,width=0.45\linewidth]{appendix/caobsgene_ICGC}
		\hfill
		\includegraphics[page=33,height=0.43\linewidth,width=0.45\linewidth]{appendix/cacrolgene_ICGC}\\
		\caption{Heatmaps showing the association of the other CR obesity metagenes with the sample gene expression from the \gls{icgc} \gls{skcm} data set.
		Scales, p-values and $R^2$-value are as described in previous figures.}
		\label{fig:degmetaicgc_skcm}
	\end{figure}

	\begin{figure}[htpb]
		\ContinuedFloat
		\captionsetup{list=off,format=cont}
		\centering
		\includegraphics[page=33,height=0.42\linewidth,width=0.45\linewidth]{appendix/caresobsgene_ICGC}
		\hfill
		\includegraphics[page=33,height=0.42\linewidth,width=0.45\linewidth]{appendix/carescrolgene_ICGC}\\
		\caption{Name}
	\end{figure}

	\begin{figure}[!htpb]
		\centering
		\includegraphics[page=34,width=0.40\linewidth]{appendix/rawobsgene_ICGC}
		\hfill
		\includegraphics[page=35,width=0.40\linewidth]{appendix/rawobsgene_ICGC}\\
		\includegraphics[page=34,width=0.40\linewidth]{appendix/crolgene_ICGC}
		\hfill
		\includegraphics[page=35,width=0.40\linewidth]{appendix/crolgene_ICGC}\\
		\caption{Box plots and scatter plots showing the association of the other CR obesity metagenes with the sample \gls{bmi} status  and \gls{bmi} from the \gls{icgc} \gls{skcm} data set, respectively.
	P-values and $R^2$-value are as described in previous figures.}
		\label{fig:appendix/cr_ob_meta_box_scatter_skcm}
	\end{figure}

	\begin{figure}[htpb]
		\ContinuedFloat
		\captionsetup{list=off,format=cont}
		\centering
		\includegraphics[page=34,width=0.45\linewidth]{appendix/resobsgene_ICGC}
		\hfill
		\includegraphics[page=35,width=0.45\linewidth]{appendix/resobsgene_ICGC}\\
		\includegraphics[page=34,width=0.45\linewidth]{appendix/rescrolgene_ICGC}
		\hfill
		\includegraphics[page=35,width=0.45\linewidth]{appendix/rescrolgene_ICGC}\\
		\includegraphics[page=34,width=0.45\linewidth]{appendix/caobsgene_ICGC}
		\hfill
		\includegraphics[page=35,width=0.45\linewidth]{appendix/caobsgene_ICGC}\\
		\caption{Name}
	\end{figure}

	\begin{figure}[htpb]
		\ContinuedFloat
		\captionsetup{list=off,format=cont}
		\centering
		\includegraphics[page=34,width=0.45\linewidth]{appendix/cacrolgene_ICGC}
		\hfill
		\includegraphics[page=35,width=0.45\linewidth]{appendix/cacrolgene_ICGC}\\
		\includegraphics[page=34,width=0.45\linewidth]{appendix/caresobsgene_ICGC}
		\hfill
		\includegraphics[page=35,width=0.45\linewidth]{appendix/caresobsgene_ICGC}\\
		\includegraphics[page=34,width=0.45\linewidth]{appendix/carescrolgene_ICGC}
		\hfill
		\includegraphics[page=35,width=0.45\linewidth]{appendix/carescrolgene_ICGC}\\
		\caption{Name}
	\end{figure}

	\newpage

	\subsubsection{\gls{ucec}}
	\label{ssub:ucec}

	\begin{figure}[htp!]
		\centering
		\includegraphics[page=38,height=0.43\linewidth,width=0.45\linewidth]{appendix/rawobsgene_ICGC}
		\hfill
		\includegraphics[page=38,height=0.43\linewidth,width=0.45\linewidth]{appendix/crolgene_ICGC}\\
		\includegraphics[page=38,height=0.43\linewidth,width=0.45\linewidth]{appendix/resobsgene_ICGC}
		\hfill
		\includegraphics[page=38,height=0.43\linewidth,width=0.45\linewidth]{appendix/rescrolgene_ICGC}\\
		\includegraphics[page=38,height=0.43\linewidth,width=0.45\linewidth]{appendix/caobsgene_ICGC}
		\hfill
		\includegraphics[page=38,height=0.43\linewidth,width=0.45\linewidth]{appendix/cacrolgene_ICGC}\\
		\caption{Heatmaps showing the association of the other CR obesity metagenes with the sample gene expression from the \gls{icgc} \gls{ucec} data set.
		Scales, p-values and $R^2$-value are as described in previous figures.}
		\label{fig:degmetaicgc_ucec}
	\end{figure}

	\begin{figure}[htpb]
		\ContinuedFloat
		\captionsetup{list=off,format=cont}
		\centering
		\includegraphics[page=38,height=0.42\linewidth,width=0.45\linewidth]{appendix/caresobsgene_ICGC}
		\hfill
		\includegraphics[page=38,height=0.42\linewidth,width=0.45\linewidth]{appendix/carescrolgene_ICGC}\\
		\caption{Name}
	\end{figure}

	\begin{figure}[!htpb]
		\centering
		\includegraphics[page=39,width=0.40\linewidth]{appendix/rawobsgene_ICGC}
		\hfill
		\includegraphics[page=40,width=0.40\linewidth]{appendix/rawobsgene_ICGC}\\
		\includegraphics[page=39,width=0.40\linewidth]{appendix/crolgene_ICGC}
		\hfill
		\includegraphics[page=40,width=0.40\linewidth]{appendix/crolgene_ICGC}\\
		\caption{Box plots and scatter plots showing the association of the other CR obesity metagenes with the sample \gls{bmi} status  and \gls{bmi} from the \gls{icgc} \gls{ucec} data set, respectively.
	P-values and $R^2$-value are as described in previous figures.}
		\label{fig:appendix/cr_ob_meta_box_scatter_ucec}
	\end{figure}

	\begin{figure}[htpb]
		\ContinuedFloat
		\captionsetup{list=off,format=cont}
		\centering
		\includegraphics[page=39,width=0.45\linewidth]{appendix/resobsgene_ICGC}
		\hfill
		\includegraphics[page=40,width=0.45\linewidth]{appendix/resobsgene_ICGC}\\
		\includegraphics[page=39,width=0.45\linewidth]{appendix/rescrolgene_ICGC}
		\hfill
		\includegraphics[page=40,width=0.45\linewidth]{appendix/rescrolgene_ICGC}\\
		\includegraphics[page=39,width=0.45\linewidth]{appendix/caobsgene_ICGC}
		\hfill
		\includegraphics[page=40,width=0.45\linewidth]{appendix/caobsgene_ICGC}\\
		\caption{Name}
	\end{figure}
